Method to infer relatedness using low coverage ancient DNA

### 2021-12-13 paper_overleaf/main.tex
started supplementary info section
added figure legends in results

\begin{figure}[htp]
    \centering
    \includegraphics[width=18cm]{plots/plotimg/ROHplot.png}
    \caption{ROH stuff}
    \label{fig:galaxy}
\end{figure}

@@

\begin{figure}[htp]
    \centering
    \includegraphics[width=18cm]{plots/plotimg/contam0_inbred0_model_performance_allroc_asc0_plot.png}
    \caption{cutoff stuff}
    \label{fig:galaxy}
\end{figure}

@@

\begin{figure}[htp]
    \centering
    \includegraphics[width=18cm]{plots/plotimg/comparison_plot.png}
    \caption{comparison stuff}
    \label{fig:galaxy}
\end{figure}

@@

\begin{figure}[htp]
    \centering
    \includegraphics[width=18cm]{plots/plotimg/fil0_relatable_plot.png}
    \caption{Chagyrskaya stuff}
    \label{fig:galaxy}
\end{figure}

@@

>>>>

\begin{figure}[htp]
    \centering
    \includegraphics[width=18cm]{plots/plotimg/ROHplot.png}
    \caption{Estimation of ROH probabilities along the genome. Top panel shows proportion of differences along the genome, and the bottom panel shows probability of no ROH. A.Simulation with no ascertainment, contamination, or ROH. B. Simulation with ROH C. Simulation with ROH and ascertainment D. Simulation with ascertainment}
    \label{fig:galaxy}
\end{figure}

@@

\begin{figure}[htp]
    \centering
    \includegraphics[width=18cm]{plots/plotimg/contam0_inbred0_model_performance_allroc_asc0_plot.png}
    \caption{False positive and negative rates as a function of cutoff on log likelihood ratio. Dotted line represents $5\%$$}
    \label{fig3}
\end{figure}

@@

\begin{figure}[htp]
    \centering
    \includegraphics[width=18cm]{plots/plotimg/comparison_plot.png}
    \caption{Comparison of KIn with READ using simulations with different coverages, and different cases of ascertainment, contamination and ROH}
    \label{fig4}
\end{figure}

@@

\begin{figure}[htp]
    \centering
    \includegraphics[width=18cm]{plots/plotimg/fil0_relatable_plot.png}
    \caption{Application of KIn on Neandertal specimens from Chagyrskaya}
    \label{fig5}
\end{figure}

@@

\section{Supplementary Information}
-binomial,betabinomial
